---
title: "Accessing stock data with R"
author: "Richard Warnung"
date: "August 12, 2022"
---
# Introduction
This is a short introduction to the [R package yfR](https://ropensci.org/blog/2022/07/26/package-yfr/)
Required packages: yfr, lubridate, dplyr, ggplot2

# Installation

```{r eval=FALSE}

# CRAN (stable)
install.packages('yfR')

# GitHub (dev version)
devtools::install_github('ropensci/yfR')

# rOpenSci
install.packages("yfR", repos = c("https://ropensci.r-universe.dev", "https://cloud.r-project.org"))
```

# From the vignette
## Retrieve historical data of S&P 500    

```{r }

pacman::p_load(yfR, lubridate, dplyr)

# set options for algorithm
my_ticker = '^GSPC'
first_date = "1950-01-01"
last_date = Sys.Date()

# fetch data
df_yf = yf_get(tickers = my_ticker, 
                first_date = first_date,
                last_date = last_date)

# output is a tibble with data
glimpse(df_yf)
```

The total return can be calculated based on the the adjusted price

```{r }

n_years = interval(min(df_yf$ref_date), max(df_yf$ref_date))/years(1)

total_return = last(df_yf$price_adjusted)/first(df_yf$price_adjusted) - 1

cat(paste0("n_years = ", n_years, "\n",
           "total_return = ", total_return))

## check
last(df_yf$cumret_adjusted_prices)
```

Additionally, we can calculate the average annual return

```{r }
ret_comp <- (1 + total_return)^(1/n_years)  - 1

cat(paste0("Comp Return = ",
           scales::percent(ret_comp, accuracy = 0.01)))

## checking:
(1+ret_comp)^n_years - 1
```

We can plot the performance like that:


```{r }

library(ggplot2)

p <- ggplot(df_yf, aes(x = ref_date, y = price_adjusted)) + 
  geom_line() +
  labs(
    title = paste0("SP500 Index Value (", 
                   year(min(df_yf$ref_date)), ' - ',
                   year(max(df_yf$ref_date)), ")"
    ),
    x = "Time", 
    y = "Index Value",
    caption = "Data from Yahoo Finance <https://finance.yahoo.com/>") + 
  theme_light() + 
  scale_y_log10() 

p
```

## Analyze many stocks
We can analyze many stocks by observing the index composition. To this aim, we sample 10 stocks from the current compoisition of the S&P 500.

```{r }

set.seed(20220713)

n_tickers <- 10
df_sp500 <- yf_index_composition("SP500")

rnd_tickers <- sample(df_sp500$ticker, n_tickers)

cat(paste0("The selected tickers are: ", paste0(rnd_tickers, collapse = ", ")))
```

Next we fetch all prices

```{r }

df_yf <- yf_get(tickers = rnd_tickers,
                first_date = '2010-01-01',
                last_date = Sys.Date())
```

One stock was removed as it was not possible to fetch sufficiently many prices. We plot the remaining ones as follows:

```{r }

p <- ggplot(df_yf, 
            aes(x = ref_date, 
                y = cumret_adjusted_prices, 
                color = ticker)) + 
  geom_line() +
  labs(
    title = paste0("SP500 Index Value (", 
                   year(min(df_yf$ref_date)), ' - ',
                   year(max(df_yf$ref_date)), ")"
    ),
    x = "Time", 
    y = "Accumulated Return (from 100%)",
    caption = "Data from Yahoo Finance <https://finance.yahoo.com/>") + 
  theme_light() + 
  scale_y_log10() 

p
```

Finally, we produce an overview table with the previous return measurements:


```{r }

library(dplyr)

tab_perf <- df_yf |>
  group_by(ticker) |>
  summarise(
    n_years = interval(min(ref_date), 
                       max(ref_date))/years(1),
    total_ret = last(price_adjusted)/first(price_adjusted) - 1,
    ret_comp = (1 + total_ret)^(1/n_years) - 1
  )

tab_perf |> 
  mutate(n_years = floor(n_years),
         total_ret = scales::percent(total_ret),
         ret_comp = scales::percent(ret_comp)) |>
  knitr::kable(caption = "Financial Performance of Several Stocks")
```

## Query many tickers with quantmod
taken from [this blog post](https://kiandlee.blogspot.com/2022/08/r-code-snippet-read-historical-prices_14.html).

```{r }
#========================================================#
# Quantitative ALM, Financial Econometrics & Derivatives 
# ML/DL using R, Python, Tensorflow by Sang-Heon Lee 
#
# https://kiandlee.blogspot.com
```
```{r -#}
# read historical prices of stock indices
#========================================================#

library(quantmod)
library(stringr) # trim

```
```{r }
# Symbols of stock indices, as of 2022-08-14
```
```{r }
vstr_symbol <- "
    Symbol    ,    Name
    ^GSPC     ,    S&P 500   
    ^DJI      ,    Dow 30
    ^IXIC     ,    Nasdaq
    ^NYA      ,    NYSE COMPOSITE (DJ)
    ^XAX      ,    NYSE AMEX COMPOSITE INDEX   
    ^BUK100P  ,    Cboe UK 100
    ^RUT      ,    Russell 2000
    ^VIX      ,    CBOE Volatility Index
    ^FTSE     ,    FTSE 100
    ^GDAXI    ,    DAX PERFORMANCE-INDEX
    ^FCHI     ,    CAC 40
    ^STOXX50E ,    ESTX 50 PR.EUR
    ^N100     ,    Euronext 100 Index
    ^BFX      ,    BEL 20
    ^N225     ,    Nikkei 225
    ^HSI      ,    HANG SENG INDEX
    000001.SS ,    SSE Composite Index
    399001.SZ ,    Shenzhen Index
    ^STI      ,    STI Index
    ^AXJO     ,    S&P/ASX 200
    ^AORD     ,    ALL ORDINARIES
    ^BSESN    ,    S&P BSE SENSEX
    ^JKSE     ,    Jakarta Composite Index
    ^KLSE     ,    FTSE Bursa Malaysia KLCI
    ^NZ50     ,    S&P/NZX 50 INDEX GROSS
    ^KS11     ,    KOSPI Composite Index
    ^TWII     ,    TSEC weighted index
    ^GSPTSE   ,    S&P/TSX Composite index
    ^BVSP     ,    IBOVESPA
    ^MXX      ,    IPC MEXICO   
    ^TA125.TA ,    TA-125   
    ^JN0U.JO  ,    Top 40 USD Net TRI Index
    "

```
```{r }
# split symbols and make vector
```
```{r }
df <- read.table(text = str_trim(vstr_symbol), 
                 sep = ",", header = TRUE)
df <- as.data.frame(df); df

df$Symbol <- str_trim(gsub("[\t\r\n,]", "", df$Symbol))
df$Name   <- str_trim(gsub("[\t\r\n,]", "", df$Name))
df
nc <- nrow(df) # number of index

```
```{r }
# read price information
```
```{r }
sdate <- as.Date("2016-01-01")
edate <- as.Date("2022-08-12")
getSymbols(df$Symbol, from=sdate, to=edate)

```
```{r }
# collect only adjusted prices
```
```{r }
price <- NULL
for(i in 1:nc) {
  eval(parse(text=paste0(
    "price <- cbind(price,`",
    gsub("\\^","",df$Symbol[i]),"`[,6])")))
}

# modify column Name as only symbol
colnames(price) <- gsub(".Adjusted", "", 
                        colnames(price))

# convert to data.frame with the first column as Date
df.price <- cbind(time=time(price), as.data.frame(price))
rownames(df.price) <- NULL

# partial selection of complete cases 
# by S&P 500, Nikkei 225, HANG SENG INDEX
df.price <- df.price[complete.cases(
  df.price[,c("GSPC","N225","HSI")]),]

```
```{r }
# print time series of daily prices
```
```{r }
head(df.price,3)
tail(df.price,3)
```

## Query exchange rates using quantmod
taken from [this blog post](https://kiandlee.blogspot.com/2022/08/r-code-snippet-read-historical-daily.html).

```{r }
library(quantmod)
library(stringr) # trim

```
```{r }
# Symbols of exchange rates, as of 2022-08-14
```
```{r }
vstr_symbol <- "
    Symbol  ,    Name
    EURUSD=X,    EUR/USD   
    JPY=X   ,    USD/JPY  
    GBPUSD=X,    GBP/USD
    AUDUSD=X,    AUD/USD
    NZDUSD=X,    NZD/USD
    EURJPY=X,    EUR/JPY
    GBPJPY=X,    GBP/JPY
    EURGBP=X,    EUR/GBP
    EURCAD=X,    EUR/CAD
    EURSEK=X,    EUR/SEK
    EURCHF=X,    EUR/CHF
    EURHUF=X,    EUR/HUF
    CNY=X   ,    USD/CNY
    HKD=X   ,    USD/HKD
    SGD=X   ,    USD/SGD
    INR=X   ,    USD/INR
    MXN=X   ,    USD/MXN
    PHP=X   ,    USD/PHP
    IDR=X   ,    USD/IDR
    THB=X   ,    USD/THB
    MYR=X   ,    USD/MYR
    ZAR=X   ,    USD/ZAR
    RUB=X   ,    USD/RUB
    "

```
```{r }
# split symbols and make vector
```
```{r }
df <- read.table(text = str_trim(vstr_symbol), 
                 sep = ",", header = TRUE)
df <- as.data.frame(df); df

df$Symbol <- str_trim(gsub("[\t\r\n,]", "", df$Symbol))
df$Name   <- str_trim(gsub("[\t\r\n,]", "", df$Name))
df
nc <- nrow(df) # number of exchange rate

```
```{r }
# read price information
```
```{r }
sdate <- as.Date("2016-01-01")
edate <- as.Date("2022-07-31")
getSymbols(df$Symbol, from=sdate, to=edate)

```
```{r }
# collect only adjusted prices
```
```{r }
price <- NULL
for(i in 1:nc) {
  eval(parse(text=paste0(
    "price <- cbind(price,`",
    gsub("\\^","",df$Symbol[i]),"`[,6])")))
}

# modify column Name as only symbol
colnames(price) <- gsub(".X.Adjusted", "", colnames(price))

# convert to data.frame with the first column as Date
df.price <- cbind(time=time(price), as.data.frame(price))
rownames(df.price) <- NULL

```
```{r }
# print time series of daily prices
```
```{r }
head(df.price,3)
tail(df.price,3)
```

## Query crypto currencies using quantmod
taken from [this blog post](https://kiandlee.blogspot.com/2022/08/r-code-snippet-read-historical-prices.html).
It is worth noting that the quantmod R package we used in this work does not provide the full or longer history of crypto prices. 
For example the first historical data of BTC begins at 2014-09-17 and ETH at 2017-11-09. The available sample periods of other coins 
are similar to or less than that of ETH.

```{r }
library(quantmod)
library(stringr) # trim

```
```{r }
# Major cryptocurrencies, as of 2022-08-13
```
```{r }
vstr_symbol <- "
    Symbol  ,    Name
    BTC-USD  ,    Bitcoin USD        
    ETH-USD  ,    Ethereum USD   
    USDT-USD ,    Tether USD
    USDC-USD ,    USD Coin USD
    BNB-USD  ,    Binance Coin USD
    ADA-USD  ,    Cardano USD
    XRP-USD  ,    XRP USD
    BUSD-USD ,    Binance USD USD
    SOL-USD  ,    Solana USD
    HEX-USD  ,    HEX USD
    DOT-USD  ,    Polkadot USD
    DOGE-USD ,    Dogecoin USD
    AVAX-USD ,    Avalanche USD
    MATIC-USD,    Polygon USD
    DAI-USD  ,    Dai USD
    WTRX-USD ,    Wrapped TRON USD
    SHIB-USD ,    SHIBA INU USD
    STETH-USD,    Lido stETH USD
    UNI1-USD ,    Uniswap USD
    TRX-USD  ,    TRON USD
    ETC-USD  ,    Ethereum Classic USD
    WBTC-USD ,    Wrapped Bitcoin USD
    LEO-USD  ,    UNUS SED LEO USD
    LTC-USD  ,    Litecoin USD
    NEAR-USD ,    NEAR-USD
      "

```
```{r }
# split Symbol and make vector
```
```{r }
df <- read.table(text = str_trim(vstr_symbol), 
                 sep = ",", header = TRUE)
df <- as.data.frame(df); df

df$Symbol <- str_trim(gsub("[\t\r\n,]", "", df$Symbol))
df$Name   <- str_trim(gsub("[\t\r\n,]", "", df$Name))
df
nc <- nrow(df) # number of crypto

```
```{r }
# read price information
```
```{r }

# limitation of data length
# BTC                 : from 2014-09-17
# ETH and some coins  : from 2017-11-09
# others              : short period

sdate <- as.Date("2017-11-09")
edate <- as.Date("2022-08-12")
getSymbols(df$Symbol,from=sdate,to=edate)

```
```{r }
# collect only adjusted prices
```
```{r }
price <- NULL
for(i in 1:nc) {
  eval(parse(text=paste0(
    #"price <- cbind(price,,df$Symbol[i],,df$Symbol[i],[,6])")))
    
    "price <- cbind(price,`",
    gsub("\\^","",df$Symbol[i]),"`[,6])")))
}

# modify column name as only symbol
colnames(price) <- gsub(".USD.Adjusted", "", colnames(price))

# convert to data.frame with the first column as Date
df.price <- cbind(time=time(price), as.data.frame(price))
rownames(df.price) <- NULL

```
```{r }
# print time series of daily prices
```
```{r }
head(df.price)
tail(df.price)
```

