---
title: "Summary of the yahoofinancer package"
format: html
editor: visual
---

This document is a short summary of the functionalities of the yahoofinancer package. The information is taken from [this blog post](taken%20from%20https://blog.rsquaredacademy.com/introducing-yahoofinancer-fetch-data-from-yahoo-finance-api/). The main package of the package can be found [here (https://yahoofinancer.rsquaredacademy.com/index.html)](https://yahoofinancer.rsquaredacademy.com/index.html).

## Basic set-up and functionalities

Information is queried based on a ticker.

```{r}
library(yahoofinancer)
aapl <- Ticker$new('aapl')
validate('aapl')
```

Based on this we can query current market data

```{r}
aapl$quote$regularMarketPrice
aapl$summary_detail
```

We can also query key statistics and valuation data:

```{r}
aapl$quote$regularMarketPrice
aapl$summary_detail
head(purrr::map(aapl$key_stats, 'raw'))
aapl$valuation_measures
```

The price history can be queried like this:

```{r}
aapl$get_history(start = '2022-10-01', end = '2022-10-14', interval = '1d')

```

Balance sheet information can be queried:

```{r}
aapl$get_balance_sheet('annual')
aapl$get_income_statement('annual')
aapl$get_cash_flow()
aapl$earnings_trend$earnings_estimate
aapl$earnings_trend$revenue_estimate
```

Option data is offered:

```{r}
head(aapl$option_chain)
aapl$option_expiration_dates
aapl$option_strikes
```

Data about holding patterns and recommendations is available:\

```{r}
aapl$major_holders
aapl$recommendation_trend
```

## Indices

The index class can be used to query index data:

```{r}
nifty = Index$new('^NSEI')
nifty$summary_detail
```

As for stocks, historical quotes of indices can be queried:

```{r}
nifty$get_history(start = '2022-10-20', interval = '1d')
```

## Currencies

Currency data can be queried:

```{r}
currency_summary(from = "USD", to = "EUR")
```

with historical quotes as follows:

```{r}
hist_data = currency_converter('EUR', 'USD', '2022-03-01',  Sys.Date())
tail(hist_data)
head(hist_data)
```
